---
title: "Cabbages"
author: "Kiara"
date: "September 8, 2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction
The cabbages data from the MASS package is loaded into a data called veggy.

Complete this report by answering theses following question 

$H_0$ there is no difference in the Vitim C cultivation c39 and c52

$H_A$ there is a statistically significant amount of Victim c in ether cultivation c39 or c52 


<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results
```{r}
ggplot(veggy, aes(x = Cult, y = VitC)) +
 geom_boxplot(fill = "lavender", color = "black", notch = TRUE, outlier.colour = "red") +
  labs(x = "Cult", y = "Vitamin C")
```
per the boxplot, C52 shown a higher level of h=vitam C.

bu looking at the two you can see they are disjoint. Indicating a probability of a significant difference. 






<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results
```{r}
favstats(VitC~Cult,data=veggy)
```

the data shows that Q3 of C39 is smaller than the Q1of c52 indicating that they are indeed disjoint





<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results
```{r}
t.test(VitC~Cult,data=veggy)
```

The p-value is .00000003405. This is obviously shown in C39 and C52 these are very different from one another 



<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

when i started I Load the Required Library: Start by loading the ggplot2 library in R, which is essential for creating customized plots. Then I made sure the data set (veggy in this case) loaded or available in your R environment. after that I Create the Boxplot: Using the ggplot() function to create the boxplot and specify the dataset and aesthetics. after I finished up with that I Label Axes. then lastly I Customize Axis Labels: Optionally, use the theme() function to customize the appearance of axis labels, such as changing the color and size of the x-axis label. And last but not least Display the Plot: The boxplot chart will be displayed once you run the complete code. Then finished it all up with the  summary.




<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
